### 2025-04-15 project2/nnMetamodels.tex
s

For an inner simulation path $\Stilde_{t+1},\ldots,\Stilde_{T}$ of the \gls{gmwb} contract, the sensitivity of $V_t$ can be calculated by the following recursion:
\begin{equation}
    \sum_{s=t+1}^{T} e^{-r(T-s)} \left[\bm{1}\{\Itilde_{t,s} > \Ftilde_{t,s}\} \cdot \left( \frac{\partial \Itilde_{t,s}}{ \partial S_t} - \frac{\partial \Ftilde_{t,s}}{ \partial S_t}\right)- \eta_n \frac{\partial \Ftilde_{t,s}}{ \partial S_t}\right], \nonumber \\
    t=0,\ldots,T-1, 
\end{equation}
where $\bm{1}\{\cdot\}$ is an indicator function, $\Stilde_t = (S_{t, t+1},\ldots,S_{t, T})$, $\Ftilde_t = (F_{t, t+1},\ldots,F_{t, T})$, $\Gtilde_t = (G_{t, t+1},\ldots,G_{t, T})$, $\Itilde_t = (I_{t, t+1},\ldots,I_{t, T})$, and
\begin{align} \label{eq2:partial-derivatives}
    \frac{\partial \Ftilde_{t, s}}{ \partial S_t} &= \bm{1}\{\Itilde_{t, s-1} < \Ftilde_{t, s-1}\}\cdot\left( \frac{\partial \Ftilde_{t, s-1}}{ \partial S_t} - \frac{\partial \Itilde_{t, s-1}}{ \partial S_t}\right) \cdot \frac{\Stilde_{t, s}}{\Stilde_{t, s-1}}\cdot (1-\eta_g),\nonumber \\
    \frac{\partial \Gtilde_{t, s}}{ \partial S_t} &= \bm{1}\{\Gtilde_{t, s-1} < \Ftilde_{t, s}\}\cdot\frac{\partial \Ftilde_{t, s}}{ \partial S_t} + \bm{1}\{\Gtilde_{t, s-1} \geq \Ftilde_{t, s}\}\cdot\frac{\partial \Gtilde_{t, s-1}}{ \partial S_t},\nonumber \\
    \frac{\partial \Itilde_{t, s}}{ \partial S_t} &= \gamma \frac{\partial \Gtilde_{t, s}}{ \partial S_t}.
\end{align}
At each inner simulation, the sample path at $t$ is initialized as:
\begin{equation}
    (\tilde{X}_{t, t}) = (\tilde{S}_{t, t}, \tilde{F}_{t, t}, \tilde{G}_{t, t}) = (S_t, F_t, G_t) = (X_t)
\end{equation}
W
Before withdrawal at $t$, the partial derivatives are initialized. $\tilde{F}_{t, t}$ is set to be proportional to $\tilde{S}_{t}$, such that:
\begin{equation}
    \frac{\partial \Ftilde_{t, t}}{ \partial S_t} = \frac{\partial F_t}{ \partial S_t} = \frac{F_t}{S_t}.
\end{equation}
$\tilde{G}_{t, t}$ and $\tilde{I}_{t, t}$ are fixed as constants, such that:
\begin{equation}
    \frac{\partial \Gtilde_{t, t}}{ \partial S_t} = \frac{\partial G_{t}}{ \partial S_t} = 0, \quad \frac{\partial \Itilde_{t, t}}{ \partial S_t} = \gamma \frac{\partial I_{t}}{ \partial S_t} = 0.
\end{equation}

Note that in \eqref{eq2:partial-derivatives}, no calculation is needed for $F_t < I_t$. 
In this case, the sub-account is already depleted at time $t$ and withdrawals are not allowed.
Therefore, \gls{gmwb}'s future liabilities beyond time $t$ are no longer affected by the stock price $S_t$, so no hedging is necessary.
In other words, when $F_t < I_t$, the inner simulation can be skipped and set $\Delta_t = 0$.

@@

Consider a \gls{va} contract which delta hedge portfolio at any time~$t$, $t=0,1,\ldots,T-1$, consists of $\Delta_t$ units in the underlying stock and $B_t$ amount of a risk-free zero-coupon bond maturing at time $T$.
The value of the hedge portfolio at time~$(t-1)$ is:
\begin{equation*}
    H_{t-1} = \Delta_{t-1} S_{t-1} + B_{t-1},
\end{equation*}
where $S_t$ is an underlying stock price and any time $t>0$.
This hedge portfolio is brought forward to the next rebalancing time~$t$, when its value becomes:
\begin{equation*}
    H_{t}^{bf} = \Delta_{t-1} S_{t} + B_{t-1}e^{r}.
\end{equation*}
Therefore, the time~$t$ hedging error, which is the cash flow incurred by the insurer due to rebalancing at time~$t$, is
\begin{equation}\label{eq2:hedgingerror}
    HE_t = H_t - H^{bf}_t, \quad t=1,\ldots, T-1.
\end{equation}
The \gls{pl} of the \gls{va} contract includes cost of the initial hedge ($H_0$), hedging errors~\eqref{eq2:hedgingerror}, unwinding of the hedge at maturity ($H^{bf}_T$), and unhedged liability ($V_0$).
Mathematically, the present value of these cash flows is given by
\begin{equation}\label{eq2:lossrv}
L = H_0 + \sum_{t=1}^{T-1} e^{-rt} HE_t - e^{-rT} H^{bf}_T + V_0 = \sum_{t=0}^{T-1}\Delta_t (e^{-rt}S_t - e^{-r(t+1)}S_{t+1}) + V_0,
\end{equation}
where the second equality holds by a telescopic sum simplification of $e^{-rt}B_t$, $t=0,\ldots,T-1$.

>>>>

For an inner simulation path $\Stilde_{t+1},\ldots,\Stilde_{T}$ of the \gls{gmwb} contract, the sensitivity of $V_t$ can be calculated by the following recursion:
\begin{equation}
    \sum_{s=t+1}^{T} e^{-r(T-s)} \left[\bm{1}\{\Itilde_{t,s} > \Ftilde_{t,s}\} \cdot \left( \frac{\partial \Itilde_{t,s}}{ \partial S_t} - \frac{\partial \Ftilde_{t,s}}{ \partial S_t}\right)- \eta_n \frac{\partial \Ftilde_{t,s}}{ \partial S_t}\right], \nonumber \\
    t=0,\ldots,T-1, 
\end{equation}
where $\bm{1}\{\cdot\}$ is an indicator function, $\Stilde_t = (S_{t, t+1},\ldots,S_{t, T})$, $\Ftilde_t = (F_{t, t+1},\ldots,F_{t, T})$, $\Gtilde_t = (G_{t, t+1},\ldots,G_{t, T})$, $\Itilde_t = (I_{t, t+1},\ldots,I_{t, T})$, and
\begin{align} \label{eq2:partial-derivatives}
    \frac{\partial \Ftilde_{t, s}}{ \partial S_t} &= \bm{1}\{\Itilde_{t, s-1} < \Ftilde_{t, s-1}\}\cdot\left( \frac{\partial \Ftilde_{t, s-1}}{ \partial S_t} - \frac{\partial \Itilde_{t, s-1}}{ \partial S_t}\right) \cdot \frac{\Stilde_{t, s}}{\Stilde_{t, s-1}}\cdot (1-\eta_g),\nonumber \\
    \frac{\partial \Gtilde_{t, s}}{ \partial S_t} &= \bm{1}\{\Gtilde_{t, s-1} < \Ftilde_{t, s}\}\cdot\frac{\partial \Ftilde_{t, s}}{ \partial S_t} + \bm{1}\{\Gtilde_{t, s-1} \geq \Ftilde_{t, s}\}\cdot\frac{\partial \Gtilde_{t, s-1}}{ \partial S_t},\nonumber \\
    \frac{\partial \Itilde_{t, s}}{ \partial S_t} &= \gamma \frac{\partial \Gtilde_{t, s}}{ \partial S_t}.
\end{align}
At each inner simulation, the sample path at $t$ is initialized as:
\begin{equation}
    (\tilde{X}_{t, t}) = (\tilde{S}_{t, t}, \tilde{F}_{t, t}, \tilde{G}_{t, t}) = (S_t, F_t, G_t) = (X_t)
\end{equation}
Before withdrawal at $t$, the partial derivatives are initialized. $\tilde{F}_{t, t}$ is set to be proportional to $\tilde{S}_{t}$, such that:
\begin{equation}
    \frac{\partial \Ftilde_{t, t}}{ \partial S_t} = \frac{\partial F_t}{ \partial S_t} = \frac{F_t}{S_t},
\end{equation}
and $\tilde{G}_{t, t}$ and $\tilde{I}_{t, t}$ are fixed as constants, such that:
\begin{equation}
    \frac{\partial \Gtilde_{t, t}}{ \partial S_t} = \frac{\partial G_{t}}{ \partial S_t} = 0, \quad \frac{\partial \Itilde_{t, t}}{ \partial S_t} = \gamma \frac{\partial I_{t}}{ \partial S_t} = 0.
\end{equation}
Note that in Equation~\ref{eq2:partial-derivatives}, no calculation is needed for $F_t \leq I_t$. 
In this case, the sub-account is already depleted at time $t$ and withdrawals are not allowed.
Therefore, \gls{gmwb}'s future liabilities beyond time $t$ are no longer affected by the stock price $S_t$, so no hedging is necessary.
In other words, when $F_t < I_t$, the inner simulation can be skipped and set $\Delta_t = 0$.

@@

Consider hedging a \gls{va} contract whose sub-account is invested in a stock, and the hedging portfolio is rebalanced monthly.
At $t \leq T$, a dynamic equation can be specified for the sub-account value $F_t$, in the absence of withdrawals, as:
\begin{equation*}
    F_t = F_{t-1} \cdot \frac{S_t}{S_{t-1}} \cdot (1-\eta_g)
\end{equation*}
where $\eta_g> \eta_n$ is the gross rate of management fee that is deducted from the sub-account value at the end of each month.
The delta hedge portfolio at any month~$t$, $t=0,1,\ldots,T-1$, consists of $\Delta_t$ units in the underlying stock and $B_t$ amount of a risk-free zero-coupon bond maturing at $T$ months.
The value of the hedge portfolio at month~$(t-1)$ is:
\begin{equation*}
    H_{t-1} = \Delta_{t-1} S_{t-1} + B_{t-1},
\end{equation*}
where $S_t$ is an underlying stock price and any month $t>0$.
Assuming there is no rebalacing between $t-1$ and $t$, this hedge portfolio is brought forward to month~$t$,.
Its value at month~$t$ becomes:
\begin{equation*}
    H_{t}^{bf} = \Delta_{t-1} S_{t} + B_{t-1}e^{-rt}.
\end{equation*}
Therefore, the time~$t$ hedging error, which is the cash flow incurred by the insurer due to rebalancing at time~$t$, is
\begin{equation}\label{eq2:hedgingerror}
    HE_t = H_t - H^{bf}_t, \quad t=1,\ldots, T-1.
\end{equation}
The \gls{pl} of the \gls{va} contract includes cost of the initial hedge ($H_0$), hedging errors~\eqref{eq2:hedgingerror}, unwinding of the hedge at maturity ($H^{bf}_T$), and unhedged liability ($V_0$).
Mathematically, the present value of these cash flows is given by
\begin{equation}\label{eq2:lossrv}
L = H_0 + \sum_{t=1}^{T-1} e^{-rt} HE_t - e^{-rT} H^{bf}_T + V_0 = \sum_{t=0}^{T-1}\Delta_t (e^{-rt}S_t - e^{-r(t+1)}S_{t+1}) + V_0,
\end{equation}
where the second equality holds by a telescopic sum simplification of $e^{-rt}B_t$, $t=0,\ldots,T-1$.
